\chapter{Graph}

\code{Dijkstra}{graph/dijkstra.cpp}

\codeWithDescription{Bellmanford}{graph/bellmanford.cpp}
[Calculates shortest paths from $s$ in a graph that might have negative edge weights. Unreachable nodes get \texttt{dist = inf}; nodes reachable through negative-weight cycles get \texttt{dist = -inf}. Assumes $V^2 \max |w| < \infty$ to prevent overflow. \\
\textbf{Time:} {$O(VE)$}]

\codeWithDescription{Biconnected Component}{graph/biconnectedcomp.cpp}
[Finds all biconnected components in an undirected graph and runs a callback for the edges in each. In a biconnected component, there are at least two internally disjoint paths between any two nodes. Note that a node can be in several components. An edge not in a component is a bridge. \\
\textbf{Usage:} \texttt{int eid = 0; ed.resize(N); for each (a,b): ed[a].emplace\_back(b, eid), ed[b].emplace\_back(a, eid++); bicomps([\&](const vi\& edgelist) \{...\});} \\
\textbf{Time:} {$O(E + V)$}]

\code{LCA}{graph/lca.cpp}

% \code{SCC}{graph/scc.cpp}

% Nahdi's scc
\codeWithDescription{SCC}{graph/scc_nahdi.cpp}
[ Description: Finds strongly connected components in a directed graph. 
If vertices $u, v$ belong to the same component, 
we can reach $u$ from $v$ and vice versa.]
[]
[scc(graph, (vi& v) { ... }) visits all components
 in reverse topological order. comp[i] holds the component
 index of a node (a component only has edges to components with
 lower index). ncomps will contain the number of components. O(E+V)]

\code{HLD}{graph/hld.cpp}
% \code{Heavy Light Decomposition}{graph/hld_nahdi.cpp}

\code{Centroid Decomposition}{graph/cd.cpp}
\vspace{1em}